### 2014-06-02 ACL2014/system.tex
a few minor fixes suggested by Graham

%To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
%Our framework has three main steps
%i) Generate $256$ bit signature for each query.  
%ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
%Next, generate query pairs which fall in the same table.
%iii) Compute cosine similarity between query terms which fall in the same table and return the query pairs  
%with similarity $\geq\tau$.  
%
Figure~\ref{alg:lsh} describes the algorithm for both creating the data structure, as well as for
querying it. In preprocessing step, the algorithm takes as input $N$ queries along with the associated feature vectors. 
In our setting, each query is represented using an extremely sparse and high dimensional feature vector
that is constructed as follows: for query $q$, we take all the webpages (urls) that any user has clicked on 
when querying for $q$. Using this representation, we then generate the 
$L$ different hash values for each query $q$, where each such hash value is again 
the concatenation of $K$ hash functions. These $L$ hash values per query are then used to create $L$ hash tables.
Since the width of the index of each bucket $K$, each hash table contains at most $2^K$ buckets. 
with each hash table containing at most $2^K$ buckets.
Each query term is then placed in their respective buckets for each of the $L$ hash tables.

@@

\subsection{Multi Probe \lsh}
\label{sec:mblsh}
As we discussed in Section \ref{subsec:resuseHash}, generating hash functions can be computationally expensive.
Since the memory required by the algorithm also scales linearly with $L$, the number of hash tables, it is desirable to have a small 
number of tables to reduce the memory footprint. The memory footprint of vanilla LSH is what makes it impractical for real applications. 
Here, we first describe four new variants of the vanilla \lsh algorithm motivated by the intuition in
\mblshf~\cite{LvVLDB07}. \mblshf obtains significantly higher recall than the vanilla \lsh while using
the same number of hash tables. In order to achieve this, the main intuition utilized in \mblshf is that
in addition to looking at the hash bucket that a test query $q$ falls in, it is also possible to look at the neigboring buckets
in order to find its near neigbour candidates. \mblshf in ~\cite{LvVLDB07} suggests exploring the neighboring buckets in order of the
Hamming distance from the bucket in which $q$ falls. They then empirically show that these neighboring buckets contain 
the near neighbors with very high probability. 
Although \mblshf is achieves a higher recall for the same number of hash tables, it will also require more number of 
probes since it searches for multiple buckets within a table. 
The main advantage of searching in multiple buckets over generating more number of tables 
is that it takes more memory and time to generate more tables in pre-processing.

>>>>

%To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
%Our framework has three main steps
%i) Generate $256$ bit signature for each query.  
%ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
%Next, generate query pairs which fall in the same table.
%iii) Compute cosine similarity between query terms which fall in the same table and return the query pairs  
%with similarity $\geq\tau$.  
%
Figure~\ref{alg:lsh} describes the algorithm for both creating the data structure, as well as for
querying it. In preprocessing step, the algorithm takes as input $N$ queries along with the associated feature vectors. 
In our setting, each query is represented using an extremely sparse and high dimensional feature vector
that is constructed as follows: for query $q$, we take all the webpages (urls) that any user has clicked on 
when querying for $q$. Using this representation, we then generate the 
$L$ different hash values for each query $q$, where each such hash value is again 
the concatenation of $K$ hash functions. These $L$ hash values per query are then used to create $L$ hash tables.
Since the width of the index of each bucket is $K$, each hash table contains at most $2^K$ buckets. 
Each query term is then placed in their respective buckets for each of the $L$ hash tables.

@@

\subsection{Multi Probe \lsh}
\label{sec:mblsh}
As we discussed in Section \ref{subsec:resuseHash}, generating hash functions can be computationally expensive.
Since the memory required by the algorithm also scales linearly with $L$, the number of hash tables, it is desirable to have a small 
number of tables to reduce the memory footprint. The memory footprint of vanilla LSH is what makes it impractical for real applications. 
Here, we first describe four new variants of the vanilla \lsh algorithm motivated by the intuition in
\mblshf~\cite{LvVLDB07}. \mblshf obtains significantly higher recall than the vanilla \lsh while using
the same number of hash tables. In order to achieve this, the main intuition utilized in \mblshf is that
in addition to looking at the hash bucket that a test query $q$ falls in, it is also possible to look at the neigboring buckets
in order to find its near neigbour candidates. \mblshf in ~\cite{LvVLDB07} suggests exploring the neighboring buckets in order of the
Hamming distance from the bucket in which $q$ falls. They then empirically show that these neighboring buckets contain 
the near neighbors with very high probability. 
Although \mblshf is achieves a higher recall for the same number of hash tables, it will also require more 
probes since it searches for multiple buckets within a table. 
The main advantage of searching in multiple buckets over generating more number of tables 
is that it takes more memory and time to generate more tables in pre-processing.
